Decorrelating Errors in Quantum Gates by Random Gate Synthesis

### 2018-09-22 decorrelation/decorrelation.tex
Updating Notebook with diamond norm computations, and updating the tex document a  bit

\begin{abstract}
Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical. Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods at the gate synthesis level to effect the $\amp{Why are we calling this spatial?}$spatial decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
\end{abstract}

@@

Where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$. (For the rest of this paper, we will refer to them as just depolarizing channels.) Such a channel is defined as:
\begin{equation}\label{eq:2}
  DPN[\alpha](\rho) \rightarrow (1-\alpha)\rho + \alpha\sum p_i \sigma_i\rho\sigma_i
\end{equation}
with $p_i$ summing to one. This means that on average, the unitary approximations implement the target unitary followed by a small depolarizing channel. The task of constructing the BCSs will fall to optimal control.

Because BCSs produce error channels that are depolarizing, correlations in the noise are reduced, and by generating controls that produce BCSs over a range of parameter values, a system can be made less sensitive to non-Markovian errors, e.g. drift. In addition, we will give numerical results showing that the fidelity of the new approximation to $U$ is not much worse than the fidelities of the constituent controls.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{placeholder_rb.png}
  \caption{Randomized benchmarking experiments ran using different pulse definitions. The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
  \label{fig:rb}
\end{figure}

>>>>

\begin{abstract}
Thresholds for fault-tolerant quantum computation are often calculated assuming a noise model in which errors are uncorrelated. While convenient for simulation, these error models are often unphysical. Work by Preskill and others has shown that arbitrarily long computations may be performed even in the presence of spatial correlation, provided the correlation is sufficiently weak and decays sufficiently quickly with distance, but at the cost of a significantly lower threshold. The success of algebraic decorrelation methods, such as dynamical decoupling, demonstrate that quantum control techniques are capable of reducing temporal noise correlations. We propose to introduce similar methods at the gate synthesis level to effect the temporal decorrelation of errors in quantum circuits, thereby increasing the threshold for fault-tolerant computation in such systems.
\end{abstract}

@@

Where $DPN[\alpha](\rho)$ is a \textit{generalized} depolarizing noise channel with strength $\alpha$. (For the rest of this paper, we will refer to them as just depolarizing channels.) Such a channel is defined as:
\begin{equation}\label{eq:2}
  DPN[\alpha](\rho) \rightarrow (1-\alpha)\rho + \alpha\sum p_i \sigma_i\rho\sigma_i
\end{equation}
with $p_i$ summing to one. This means that on average, the unitary approximations implement the target unitary followed by a small depolarizing channel.

One property of BCSs is that if each approximation of the target gate is correct to within $\epsilon$ in operator norm and $\alpha\leq\epsilon^2$, then the diamond distance of the BCS to $U_T$ is also no larger than $\epsilon^2$. This follows from the mixing lemma proven by Campbell and Hastings in \cite{Campbell2017} and \cite{1612.01011}. This tells us that we can lower bound the worst case performance of a BCS, and because  depolarizing, correlations in the noise are reduced, and by generating controls that produce BCSs over a range of parameter values, a system can be made less sensitive to non-Markovian errors, e.g. drift. In this paper, the task of constructing the BCSs will fall to optimal control. We will give numerical results showing that the fidelity of the new approximation to $U_T$ is of the same order as the constituent controls.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{rb_data.pdf}
  \caption{Randomized benchmarking experiments ran using different pulse definitions. The four plots on the left are from the incorrectly calibrated pulse, while the top right is the calibrated pulse, and the bottom right is the BCS.}
  \label{fig:rb}
\end{figure}
